---
title: Untitled
format:
  modern2-cv-pdf: default
author: Elliot Gould
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvcolor: 
  main: B83B5E
  accent: 6A2C70
jobtitle: they/them, he/him
sidebar:
  bullets:
    - PhD Candidate
    - Research Assistant & Consultant
    - Tutor / Demonstrator
  sections:
    - name: Contact
      items:
        - icon: map-marker
          text: Melbourne, Australia
        - icon: phone
          text: "+61 406680382"
        - icon: envelope
          text: elliot.gould@unimelb.edu.au
        - icon: github
          text: egouldo
          href: https://github.com/egouldo
    - name: Education
      items:
        - text: "Doctor of Philosophy, Science"
          inst: "University of Melbourne"
          time: "December 2017 - Present"
          details: 'Thesis: "Reproducibility and Transparency of Ecological Models in Applied Ecology and Conservation Science"'
        - text: "Master of Science (Distinction)"
          inst: "University of Melbourne"
          time: "2012 - 2015"
          details: 'Thesis: "Managing Grasslands with Models: Resolving uncertainty and allocating effort among a suite of sites."'
        - text: "Bachelor of Science"
          inst: "University of Melbourne"
          time: "2005 - 2011"
          details: "Major in Ecology, First Class Honours Average."
        - text: "Bachelor of Arts"
          inst: "University of Melbourne"
          time: "2005 - 2011"
          details: "Major in Indonesian, First Class Honours Average."
    - name: Service
      items:
        - text: "Preregistration Template Working Group Member"
          inst: "Centre for Open Science"
          time: "2023 - Present"
          details: "[The Preregistration Template Working Group](https://www.cos.io/blog/new-working-group-seeks-to-curate-and-evaluate-preregistration-templates) seeks to: 1. Establish criteria to evaluate the suitability of new preregistration templates for inclusion in the Open Science Framework (OSF); 2. Develop a procedure by which community creators of preregistration templates can put templates forward for inclusion in OSF; 3. Advise and inform COS on issues related to preregistration implementation in OSF."
        - text: "Founding Member, Secretary / Treasurer"
          inst: "Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE)"
          time: "2020 - 2023"
          details: "SORTEE is a service organization which brings together researchers working to improve reliability and transparency through cultural and institutional changes in ecology, evolutionary biology, and related fields broadly defined."
execute: 
  echo: false
---

```{r}
#| label: cvevents
#| message: false
cvevents <- function(tbl, when, what, where, descr) {

    command_start <- "\\cvevent"
    tbl[[where]] <- gsub("\n", " \\\\newline ", tbl[[where]])
    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}",
        "{", tbl[[descr]], "}"
        )

    cat(res, sep = "\n\n\n")
}

cvproj <- function(tbl,what,role,items){
    command_start <- "\\cvproj"
    res <- paste0(
        command_start, "{", tbl[[what]], "}",
        "{", tbl[[role]], "}",
        "{", sapply(tbl[[items]], function(x)paste0(x,collapse = ", ")), "}"
    )

    cat(res, sep = "\n\n\n")
}

library(dplyr)
library(purrr)

cvteaching <- function(tbl, role, subject, years, where){
  command_start <- "\\cvevent"
  
  tbl_reshaped <- tbl %>%  
    reframe(years = flatten_dbl(years),
               .by = c(role, subject, where)) %>% 
    mutate(when = glue::glue(min(years), max(years), .sep = " - "), 
           .by = role, where) %>% 
    reframe(years = paste0(years, collapse = ", "), 
            .by = c(role, when, subject, where))
  
  tbl_items <- 
    tbl_reshaped %>% 
    reframe(items = glue::glue("\\item [{subject}] {years}") %>% 
              glue::glue_collapse(sep = "") %>%
              paste("\\begin{description}[font=$\\bullet$~\\scshape\\color{maincol!50!black}]", ., "\\end{description}", 
                    sep = ""), 
            .by = "role") 
  
  res <- paste0(
        command_start, "{", pluck(tbl_reshaped, "when", unique), "}",
        "{", pluck(tbl_reshaped, role, unique), "}",
        "{", pluck(tbl_reshaped, where, unique), "}",
         "{", pluck(tbl_items, "items"), "}"
        )
  cat(res, sep = "\n\n\n")
}
```

# Summary

"Elliot Gould is a PhD candidate at the School of Agriculture, Food and Ecosystem Sciences, and a Quantitative Research Assistant on the [repliCATS project](replicats.research.unimelb.edu.au/) at the School of History and Philosophical Studies, University of Melbourne. Their PhD investigates the transparency and reproducibility of ecological models in applied ecology and conservation decision-making. In their role as a Quantitative Research Assistant, Elliot managed a small team of researchers to develop a data analytics and management platform for the repliCATS project, and contributed to research on metascience. They have an enthusiasm for teaching and skill-sharing, particularly with regard to building a strong community of practice in emerging open-science methodology and computational biology within ecology and conservation. Elliot's research seeks to use data science techniques to advance the open-science movement by improving transparency and reproducibility, focussing on ecology and conservation Science. Other research interests include decision-theory, Structured Decision Making, and plant ecology (especially grassy woodlands & grasslands of the Victorian Volcanic Plains)."

# Employment

### Research

```{r}
#| label: research
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details,
    "Consultant Ecological Modeller", "Department of Environment Land Water and Planning\nVictorian Government", "March 2020 - Present", "This research consultancy comprises a component of my PhD, aiming to test and develop preregistration templates for ecology and conservation using a case study of environmental flows management in Victoria, Australia. I designed and delivered a collaborative workshop with DEECA staff, analysed and visualised environmental flow and modelled vegetation outcome data.",
    "Quantitative Research Assistant - repliCATS, SCORE Program", "School of Historical and Philosophical Studies,\n School of BioSciences\nUniversity of Melbourne", "2019 - 2024",
    "Systematising Confidence in Open Research and Evidence (SCORE) is a Research Program initiated by the Defense Advanced Research Projects Agency  (DARPA) that aims to develop and deploy automated tools to assign 'confidence scores' to Social and Behavioural research results and claims in light of recent evidence about the 'Replication Crisis' besetting Science. The repliCATS project is one team within the SCORE project, based in Melbourne. In this role, Elliot lead a small team within the repliCATS project to build data analysis software and infrastructure to manage and deliver data products to internal teams and external partners. Research components of the role include modelling to investigate predictors of replication success.",
    "Research Assistant, Various Roles", "School of BioSciences, School of Geography\nUniversity of Melbourne", "2015 - Present", "National Environmental Science Programme, Threatened Species Recovery Hub: Conservation actions for Threatened Ecological Communities. Various plant ecology and Structured Decision Making projects, involving: data analysis and visualisations, building shiny Apps, model building and testing." 
) |>
    cvevents(when = "dates", 
             what = "role", 
             where = "institution", 
             descr = "details")
```


### Teaching


```{r}
#| label: teaching
#| output: asis
#| eval: true
tibble::tribble(
    ~role, ~subject, ~years, ~where,
    "Demonstrator, Tutor", "Environmental Risk Assessment", c(2016, 2017, 2018, 2022, 2023, 2024), "University of Melbourne",
    "Demonstrator, Tutor", "Vegetation Management \\& Conservation", c(2018, 2019), "University of Melbourne",
    "Demonstrator, Tutor", "Applied Ecology", c(2014, 2015), "University of Melbourne",
    "Demonstrator, Tutor", "Biology of Cells \\& Organisms", c(2012, 2013,2014,2015), "University of Melbourne",
    "Guest Lecturer", "Biometry", c(2023), "University of Melbourne",
    "Guest Lecturer", "Critical Thinking with Data", c(2021), "University of Melbourne"
)  %>%  cvteaching(role = "role", 
                   subject = "subject", 
                   years = "years", 
                   where = "where")
```


# Projects

See my [github profile](https://github.com/egouldo) for a comprehensive list of open source projects.
```{r}
#| label: learning_design
#| output: asis
#| eval: true
tibble::tribble(
    ~role, ~subject, ~year, ~details,
    "Learning Module Design \\& Delivery: Vegetation Management \\& Conservation", "School of BioSciences, University of Melbourne", 2019, "I co‐developed a teaching and learning module, and developed and delivered a workshop teaching the basics of data‐science in R using data collected by the students.") %>% 
  cvevents(when = "year", 
           what = "role", 
           where = "subject", 
           descr = "details")
```
# Scholarships and Awards

```{r}
#| label: awards
#| output: asis
#| eval: false
tibble::tribble(
  ~award, ~institution, ~items,
  "Science Abroad Travelling Scholarships, 2023", "University of Melbourne, Faculty of Science, School of Ecosystem and Forest Sciences", c("This scholarship supports PhD students in the Faculty of Science undertaking travel to attend conferences, fieldwork, etc. as part of a Study Away request."),
  "blah", "blah", c("blah"),
  "blah", "blah", c("blah"),
  "blah", "blah", c("blah")
) |>
  cvproj(what = "award", role = "institution", items = "items")
```


